{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-07-29 paper/tex/sections/appendix.tex
move figures around into more sensible positions
add quick links to plots

\subsection{Average target formation rate}
Double compact object formation is metallicity dependent, so we find the average rate as the integral over metallicity, which is given by
\begin{equation}\label{eq:norm_avg_target_formation}
    \avg{ \mathcal{R}_{\rm target} } = \int_{Z_{\rm min}}^{Z_{\rm max}} p_{Z} \mathcal{R}_{\rm target, Z} \dd{Z},
\end{equation}
where $Z_{\rm min}, Z_{\rm max}$ are the minimum and maximum sampled metallicities, $p_Z$ is the probability of forming a star at the metallicity $Z$ (which can be found using the distribution in \citealp{Frankel+2018}) and $\mathcal{R}_{\rm target, Z}$ is the number of targets formed per star forming mass,
\begin{equation}
    \mathcal{R}_{\rm target, Z} =  \frac{N_{\rm target, Z}}{ M_{\rm SF, Z} }.
\end{equation}
In practice, this integral is instead approximated as a sum over the metallicity bins that we use in our simulation. The number of targets in our sample at a metallicity $Z$, $N_{\rm target, Z}$, can be written simply as the sum of the targets' weights:
\begin{equation}
    N_{\rm target, Z} = \sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i},
\end{equation}
where $w_i$ is the adaptive importance sampling weight assigned to the binary by STROOPWAFEL, $N_{\rm binaries, Z}$ is the number of binaries at metallicity $Z$ in our sample and $\theta_{\rm target, i}$ is a step function that is only $1$ when the binary is a target and otherwise $0$.

The total star forming mass at a metallicity $Z$, $M_{\rm SF, Z}$, can be written as
\begin{equation}
    M_{\rm SF, Z} = \frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i,
\end{equation}
where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in our sample and $f_{\rm trunc}$ is the fraction of the total stellar mass from which COMPAS samples, given its truncated mass and separation ranges (see Section \ref{sec:COMPAS_explained}). These truncations mean that only $f_{\rm trunc} \approx 0.17$ of the stellar mass in the galaxy is sampled from and the rest is contained in lower mass stars that are not relevant for forming the DCOs studies in this paper.

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{../figures/fig11_random_simple_galaxy.png}
    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.}
    \label{fig:simple_mw}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{../figures/fig12_mBH_simple_mw_variation.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}. Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions} for comparison.}
    \label{fig:bh_mass_simple_mw}
\end{figure}

@@

\subsection{Detection rate table}
\begin{table*}[htb]
    \centering
    \caption{The number of detectable binaries in a 4- and 10-year LISA mission for the \nModels{} different model variations and each DCO type. Each value shows the mean and the 1-$\sigma$ Poisson uncertainty.}
    \begin{tabular}{cl|lll|lll}
        \hline
        \multirow{2}{*}{Model} & \multirow{2}{*}{Description} & \multicolumn{3}{c|}{LISA detections (4 year)} & \multicolumn{3}{c}{LISA detections (10 year)} \\ \cline{3-8}
        & & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
        \hline
        A & Fiducial & \confinv{73.7}{8.7}{8.3} & \confinv{42.1}{6.1}{6.9} & \confinv{7.9}{2.9}{3.1}\\
        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{68.6}{8.6}{8.4} & \confinv{22.3}{4.3}{4.7} & \confinv{2.9}{1.9}{2.1}\\
        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{46.8}{6.8}{7.2} & \confinv{8.2}{3.2}{2.8} & \confinv{3.9}{1.9}{2.1}\\
        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{46.8}{6.8}{7.2} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3}\\
        E & Case BB mass transfer is always unstable & \confinv{69.0}{8.0}{8.0} & \confinv{7.2}{2.2}{2.8} & \confinv{0.2}{0.2}{0.8}\\
        F & Model E + Model K & \confinv{153.8}{12.8}{12.2} & \confinv{147.8}{11.8}{12.2} & \confinv{18.2}{4.2}{3.8}\\
        G & CE efficiency $\alpha = 0.1$ & \confinv{27.8}{4.8}{5.2} & \confinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8}\\
        H & CE efficiency $\alpha = 0.5$ & \confinv{61.7}{7.7}{8.3} & \confinv{28.1}{5.1}{4.9} & \confinv{6.2}{2.2}{2.8}\\
        I & CE efficiency $\alpha = 2.0$ & \confinv{71.6}{8.6}{8.4} & \confinv{38.1}{6.1}{5.9} & \confinv{31.1}{5.1}{5.9}\\
        J & CE efficiency $\alpha = 10.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0}\\
        K & HG donor stars initiating a CE survive CE & \confinv{154.1}{12.1}{12.9} & \confinv{58.9}{7.9}{8.1} & \confinv{9.6}{2.6}{3.4}\\
        L & Fryer rapid SN remnant mass prescription & \confinv{50.2}{7.2}{6.8} & \confinv{70.0}{8.0}{8.0} & \confinv{6.6}{2.6}{2.4}\\
        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{95.9}{9.9}{10.1} & \confinv{30.0}{5.0}{5.0} & \confinv{7.1}{3.1}{2.9}\\
        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{58.1}{8.1}{7.9} & \confinv{51.7}{6.7}{7.3} & \confinv{8.2}{3.2}{2.8}\\
        O & PISN and pulsational-PISN not implemented & \confinv{75.1}{9.1}{8.9} & \confinv{43.2}{6.2}{6.8} & \confinv{7.9}{2.9}{3.1}\\
        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{82.4}{9.4}{8.6} & \confinv{86.3}{9.3}{9.7} & \confinv{15.4}{4.4}{3.6}\\
        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{91.5}{9.5}{9.5} & \confinv{142.4}{12.4}{11.6} & \confinv{33.4}{5.4}{5.6}\\
        R & Black holes receive not natal kick & \confinv{85.9}{8.9}{9.1} & \confinv{95.8}{9.8}{10.2} & \confinv{9.7}{2.7}{3.3}\\
        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{75.4}{8.4}{8.6} & \confinv{33.9}{5.9}{6.1} & \confinv{8.8}{2.8}{3.2}\\
        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{14.9}{3.9}{4.1} & \confinv{9.6}{3.6}{3.4}\\
        \hline
    \end{tabular}
    \label{tab:detection_rates}
\end{table*}

\subsection{Distribution of eccentric sources on sensitivity curve}
\begin{figure*}[hb]
    \centering
    \includegraphics[width=\textwidth]{fig13_dcos_on_sc_eccentric_colours.png}
    \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity. We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$.}
    \label{fig:dcos_on_sc_ecc_col}
\end{figure*}

@@

\begin{figure}[thb]
    \centering
    \includegraphics[width=\textwidth]{fig14_formation_channels.pdf}
    \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations. Channels are described in detail in \citet{Broekgaarden+2021}. The classic, single core CEE and double core CEE channels all require at least one common envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary. \todo{Update H, I, J, K, T}}
    \label{fig:formation_channels}
\end{figure}

>>>>

\subsection{Average target formation rate}
Double compact object formation is metallicity dependent, so we find the average rate as the integral over metallicity, which is given by
\begin{equation}\label{eq:norm_avg_target_formation}
    \avg{ \mathcal{R}_{\rm target} } = \int_{Z_{\rm min}}^{Z_{\rm max}} p_{Z} \mathcal{R}_{\rm target, Z} \dd{Z},
\end{equation}
where $Z_{\rm min}, Z_{\rm max}$ are the minimum and maximum sampled metallicities, $p_Z$ is the probability of forming a star at the metallicity $Z$ (which can be found using the distribution in \citealp{Frankel+2018}) and $\mathcal{R}_{\rm target, Z}$ is the number of targets formed per star forming mass,
\begin{equation}
    \mathcal{R}_{\rm target, Z} =  \frac{N_{\rm target, Z}}{ M_{\rm SF, Z} }.
\end{equation}
In practice, this integral is instead approximated as a sum over the metallicity bins that we use in our simulation. The number of targets in our sample at a metallicity $Z$, $N_{\rm target, Z}$, can be written simply as the sum of the targets' weights:
\begin{equation}
    N_{\rm target, Z} = \sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i},
\end{equation}
where $w_i$ is the binary's adaptive importance sampling weight assigned, $N_{\rm binaries, Z}$ is the number of binaries at metallicity $Z$ in our sample and $\theta_{\rm target, i}$ is only $1$ when the binary is a target and otherwise $0$.

The total star forming mass at a metallicity $Z$, $M_{\rm SF, Z}$, can be written as
\begin{equation}
    M_{\rm SF, Z} = \frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i,
\end{equation}
where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in our sample and $f_{\rm trunc}$ is the fraction of the total stellar mass from which COMPAS samples, given its truncated mass and separation ranges (see Section \ref{sec:COMPAS_explained}). These truncations mean that only $f_{\rm trunc} \approx 0.17$ of the stellar mass in the galaxy is sampled from.

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{../figures/fig11_random_simple_galaxy.png}
    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.  \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig11_random_simple_galaxy.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
    \label{fig:simple_mw}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{../figures/fig12_mBH_simple_mw_variation.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}. Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions} for comparison. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_mBH_simple_mw_variation.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:bh_mass_simple_mw}
\end{figure}

@@

\subsection{Detection rate table}
\begin{table*}[htb]
    \centering
    \caption{The number of detectable binaries in a 4- and 10-year LISA mission for the \nModels{} different model variations and each DCO type. Each value shows the mean and the 1-$\sigma$ Poisson uncertainty. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
    \begin{tabular}{cl|lll|lll}
        \hline
        \multirow{2}{*}{Model} & \multirow{2}{*}{Description} & \multicolumn{3}{c|}{LISA detections (4 year)} & \multicolumn{3}{c}{LISA detections (10 year)} \\ \cline{3-8}
        & & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
        \hline
        A & Fiducial & \confinv{73.7}{8.7}{8.3} & \confinv{42.1}{6.1}{6.9} & \confinv{7.9}{2.9}{3.1}\\
        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{68.6}{8.6}{8.4} & \confinv{22.3}{4.3}{4.7} & \confinv{2.9}{1.9}{2.1}\\
        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{46.8}{6.8}{7.2} & \confinv{8.2}{3.2}{2.8} & \confinv{3.9}{1.9}{2.1}\\
        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{46.8}{6.8}{7.2} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3}\\
        E & Case BB mass transfer is always unstable & \confinv{69.0}{8.0}{8.0} & \confinv{7.2}{2.2}{2.8} & \confinv{0.2}{0.2}{0.8}\\
        F & Model E + Model K & \confinv{153.8}{12.8}{12.2} & \confinv{147.8}{11.8}{12.2} & \confinv{18.2}{4.2}{3.8}\\
        G & CE efficiency $\alpha = 0.1$ & \confinv{27.8}{4.8}{5.2} & \confinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8}\\
        H & CE efficiency $\alpha = 0.5$ & \confinv{61.7}{7.7}{8.3} & \confinv{28.1}{5.1}{4.9} & \confinv{6.2}{2.2}{2.8}\\
        I & CE efficiency $\alpha = 2.0$ & \confinv{71.6}{8.6}{8.4} & \confinv{38.1}{6.1}{5.9} & \confinv{31.1}{5.1}{5.9}\\
        J & CE efficiency $\alpha = 10.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0}\\
        K & HG donor stars initiating a CE survive CE & \confinv{154.1}{12.1}{12.9} & \confinv{58.9}{7.9}{8.1} & \confinv{9.6}{2.6}{3.4}\\
        L & Fryer rapid SN remnant mass prescription & \confinv{50.2}{7.2}{6.8} & \confinv{70.0}{8.0}{8.0} & \confinv{6.6}{2.6}{2.4}\\
        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{95.9}{9.9}{10.1} & \confinv{30.0}{5.0}{5.0} & \confinv{7.1}{3.1}{2.9}\\
        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{58.1}{8.1}{7.9} & \confinv{51.7}{6.7}{7.3} & \confinv{8.2}{3.2}{2.8}\\
        O & PISN and pulsational-PISN not implemented & \confinv{75.1}{9.1}{8.9} & \confinv{43.2}{6.2}{6.8} & \confinv{7.9}{2.9}{3.1}\\
        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{82.4}{9.4}{8.6} & \confinv{86.3}{9.3}{9.7} & \confinv{15.4}{4.4}{3.6}\\
        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{91.5}{9.5}{9.5} & \confinv{142.4}{12.4}{11.6} & \confinv{33.4}{5.4}{5.6}\\
        R & Black holes receive not natal kick & \confinv{85.9}{8.9}{9.1} & \confinv{95.8}{9.8}{10.2} & \confinv{9.7}{2.7}{3.3}\\
        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{75.4}{8.4}{8.6} & \confinv{33.9}{5.9}{6.1} & \confinv{8.8}{2.8}{3.2}\\
        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{14.9}{3.9}{4.1} & \confinv{9.6}{3.6}{3.4}\\
        \hline
    \end{tabular}
    \label{tab:detection_rates}
\end{table*}

\subsection{Distribution of eccentric sources on sensitivity curve}
\begin{figure*}[hb]
    \centering
    \includegraphics[width=\textwidth]{fig13_dcos_on_sc_eccentric_colours.png}
    \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity. We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_dcos_on_sc_eccentric_colours.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
    \label{fig:dcos_on_sc_ecc_col}
\end{figure*}

@@

\begin{figure}[h]
    \centering
    \includegraphics[height=0.85\textheight]{fig14_formation_channels.pdf}
    \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations. Channels are described in detail in \citet{Broekgaarden+2021}. The classic, single core CEE and double core CEE channels all require at least one common envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_formation_channels.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}. \todo{Update R and T}}
    \label{fig:formation_channels}
\end{figure}

### 2021-07-29 paper/tex/sections/comparisons.tex
change all figure names to organise
add quick links to plots

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{5_compare_dco_1.png}

@@

    \includegraphics[width=\textwidth]{5_compare_dco_2.png}
    \caption{A table comparing previous studies of a similar nature to this work. The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}.}
    \label{fig:previous_studies}
\end{figure*}

>>>>

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig10_1_compare_dco.png}

@@

    \includegraphics[width=\textwidth]{fig10_2_compare_dco.png}
    \caption{A table comparing previous studies of a similar nature to this work. The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_w_compare_dco.png}{\faFileImage}.}
    \label{fig:previous_studies}
\end{figure*}

### 2021-07-29 paper/tex/sections/methods.tex
change all figure names to organise
move figures around into more sensible positions
add quick links to plots

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{1_galaxy_diagram.png}
    \caption{A schematic illustrating how we model the Milky Way. The left panel illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), radial distribution, metallicity-radius-time relation, and height distribution. The right panel shows an example instance of the Milky Way with $250000$ binaries shown as points coloured by metallicity. The top panel shows a side-on view and the bottom panel a face-on view.}
    \label{fig:galaxy_schematic}
\end{figure*}

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{fig1_galaxy_diagram.png}
    \caption{A schematic illustrating how we model the Milky Way. The left panel illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), radial distribution, metallicity-radius-time relation, and height distribution. The right panel shows an example instance of the Milky Way with $250000$ binaries shown as points coloured by metallicity. The top panel shows a side-on view and the bottom panel a face-on view. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig1_galaxy_diagram.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
    \label{fig:galaxy_schematic}
\end{figure*}

@@

### 2021-07-29 paper/tex/sections/results.tex
add quick links to plots

\subsection{The LISA sensitivity curve and the population of detectable sources}\label{sec:dcos_on_sc}
\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig2_dcos_on_sc.png}
    \caption{The LISA sensitivity curve is shown together with the density distribution of the characteristic strain and the dominant frequency for all detectable sources in our simulations (top) and separated by type (bottom). Contours show the percentage of the population enclosed. The remaining 2\% of the population is shown as dots with a size that scales with the sampling weight. To guide the interpretation, we show reference lines marking where a circular binary would reside for a given distance (diagonal line) and remaining inspiral time (vertical lines), assuming an average chirp mass $\avg{\mathcal{M}_c}$, orientation and sky location. The curved reference line shows the signal expected for an eccentric binary at 30 kpc. The coloured lines in the bottom panels show a contour that encloses 90\% of the population that is circular. LISA verification binaries are overplotted in the top panel (star symbols).  See also Fig.~\ref{fig:dcos_on_sc_ecc_col} and Sec.~\ref{sec:dcos_on_sc} for a discussion.}
    \label{fig:dcos_on_sc}
\end{figure*}
We show the expected distribution of detectable DCOs together with the LISA sensitivity curve in Fig.~\ref{fig:dcos_on_sc} for all sources combined in the top panel and separated by type in the three lower panels. For reference, we overplot dotted lines to indicate where a binary system would reside for a given distance (diagonal lines) and a remaining inspiral time (vertical lines). For each line we assume the binary is circular and has the average chirp mass of the sample ($\avg{\mathcal{M}_c}$, annotated in each panel), unless indicated otherwise. We observe several features worthwhile discussing, some that earlier studies have touched upon (see Sec.~\ref{sec:compare_studies}), as well as some new findings related to eccentricity.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{fig3_detectable_properties_4yr.pdf}
    \caption{Properties of detectable systems for a 4-year LISA mission in our fiducial model. Each panel shows a kernel density estimator for a single property, coloured by DCO type. The shaded areas show the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). The dotted lines in the black hole mass panel show the individual primary and secondary mass distributions. See Sec.~\ref{sec:fiducial_distributions} for a discussion.}
    \label{fig:fiducial_pdf_distributions}
\end{figure*}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig4_1_detectable_distance_distribution_4yr.pdf}
    \includegraphics[width=\columnwidth]{fig4_2_galaxy_density_distribution.png}
    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance. \textbf{Bottom:} A face-on view of the Galactic density distribution for detectable DCOs. We show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their sampling weights. The coloured lines show the 75\% contour for each of the individual DCO types. The large cross passes through (0, 0) and helps to highlight the bias towards the position of the sun, which is indicated by the $\odot$.}
    \label{fig:detectable_distance_dist}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig5_chirp_mass_uncertainty_4yr.pdf}
    \caption{Cumulative distribution function for error on the chirp mass. Colours indicate DCO type and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). The shaded region indicates region with unmeasureable chirp mass.}
    \label{fig:m_c_unc}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{fig6_angular_resolution_4yr.pdf}
    \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution.}
    \label{fig:ang_res}
\end{figure}

>>>>

\subsection{The LISA sensitivity curve and the population of detectable sources}\label{sec:dcos_on_sc}
\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig2_dcos_on_sc.png}
    \caption{The LISA sensitivity curve is shown together with the density distribution of the characteristic strain and the dominant frequency for all detectable sources in our simulations (top) and separated by type (bottom). Contours show the percentage of the population enclosed. The remaining 2\% of the population is shown as dots with a size that scales with the sampling weight. To guide the interpretation, we show reference lines marking where a circular binary would reside for a given distance (diagonal line) and remaining inspiral time (vertical lines), assuming an average chirp mass $\avg{\mathcal{M}_c}$, orientation and sky location. The curved reference line shows the signal expected for an eccentric binary at 30 kpc. The coloured lines in the bottom panels show a contour that encloses 90\% of the population that is circular. LISA verification binaries are overplotted in the top panel (star symbols).  See also Fig.~\ref{fig:dcos_on_sc_ecc_col} and Sec.~\ref{sec:dcos_on_sc} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig2_dcos_on_sc.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
    \label{fig:dcos_on_sc}
\end{figure*}
We show the expected distribution of detectable DCOs together with the LISA sensitivity curve in Fig.~\ref{fig:dcos_on_sc} for all sources combined in the top panel and separated by type in the three lower panels. For reference, we overplot dotted lines to indicate where a binary system would reside for a given distance (diagonal lines) and a remaining inspiral time (vertical lines). For each line we assume the binary is circular and has the average chirp mass of the sample ($\avg{\mathcal{M}_c}$, annotated in each panel), unless indicated otherwise. We observe several features worthwhile discussing, some that earlier studies have touched upon (see Sec.~\ref{sec:compare_studies}), as well as some new findings related to eccentricity.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{fig3_detectable_properties_4yr.pdf}
    \caption{Properties of detectable systems for a 4-year LISA mission in our fiducial model. Each panel shows a kernel density estimator for a single property, coloured by DCO type. The shaded areas show the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). The dotted lines in the black hole mass panel show the individual primary and secondary mass distributions. See Sec.~\ref{sec:fiducial_distributions} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig3_detectable_properties_4yr.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:fiducial_pdf_distributions}
\end{figure*}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig4_1_detectable_distance_distribution_4yr.pdf}
    \includegraphics[width=\columnwidth]{fig4_2_galaxy_density_distribution.png}
    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance. \textbf{Bottom:} A face-on view of the Galactic density distribution for detectable DCOs. We show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their sampling weights. The coloured lines show the 75\% contour for each of the individual DCO types. The large cross passes through (0, 0) and helps to highlight the bias towards the position of the sun, which is indicated by the $\odot$. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_1_detectable_distance_distribution_4yr.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_2_galaxy_density_distribution.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
    \label{fig:detectable_distance_dist}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig5_chirp_mass_uncertainty_4yr.pdf}
    \caption{Cumulative distribution function for error on the chirp mass. Colours indicate DCO type and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). The shaded region indicates region with unmeasureable chirp mass. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_chirp_mass_uncertainty_4yr.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:m_c_unc}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{fig6_angular_resolution_4yr.pdf}
    \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_angular_resolution_4yr.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:ang_res}
\end{figure}
